Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-14 doc/lean.tex

\subsection{Proof Checker}

@@

\subsection{The Model Counter}

@@

In sum, in addition to trusting Lean's foundation and trusted kernel,
we also have to trust that code extraction respects that foundation,
that the implementation of arrays and hashmaps satisfy their internal descriptions,
and that, after parsing, the computation has the correct input formula.
All of our specifications have been completely proved and verified relative to that.

>>>>

\subsection{The Proof Checker}

@@

\subsection{The Model Counters}

@@

In sum, in addition to trusting Lean's foundation and kernel checker,
we also have to trust that code extraction respects that foundation,
that the implementation of arrays and hashmaps satisfy their internal descriptions,
and that, after parsing, the computation has the correct input formula.
All of our specifications have been completely proved and verified relative to that.
